Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-25 Arxiv/main.tex
fix typos

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
	\end{equation*}
	for $z \in R_1$.

	Let $Pr[u(\hexpmech(\dataobs)) = c] = |r|  \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = |r|  \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.

	After simplification, we need to show: $u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

@@

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
		\end{equation*}
		is always true when $\lambda < 0$
	\item $\lambda > 0$

		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs))$. Then, what we need to proof under the case $\lambda > 0$ is:
		\begin{equation}
		\label{eq_dilation_case2}
		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
		\end{equation}

		Based on the accuracy property of exponential mechanism:
		\begin{equation*}
		\begin{split}
		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
		\end{split}
		\end{equation*}
		we derived the accuracy bound for $\hexpmech$:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs)) \leq c] 
		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
		\end{split}
		\end{equation*}

		apply this bound to eq. \ref{eq_dilation_case2}:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
		\end{split}
		\end{equation*}

		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.

@@

	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(\dataobs',z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,

	Given that $2\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(y,z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
	& = 	\frac{1}{|z|}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\Big)\\
	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\Big)\\
	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ z = r] + \delta,
	\end{split}
	\end{equation*}
	where the $\delta = \frac{e^{\epsilon/2} \delta'}{2|z|}$.

>>>>

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
	\end{equation*}
  we need to show:
  \begin{equation*}
  Pr[u(\hexpmech(\dataobs), \dataobs) = u(r,\dataobs)]
  \leq
  e^{\frac{\epsilon}{2}} Pr[u(\hexpmech(\dataobs), \dataobs) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
  \end{equation*}

	Let $u(r,\dataobs) = c$, $Pr[u(\hexpmech(\dataobs), \dataobs) = c] = |z|  \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs), \dataobs) = e^{\lambda} c] = |z|  \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.

	After simplification, we need to show: $u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

@@

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
		\end{equation*}
		is always true when $\lambda < 0$
	\item $\lambda > 0$

		Because $\hat{s} = u(r, \dataobs)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs), \dataobs)$. Then, what we need to proof under the case $\lambda > 0$ is:
		\begin{equation}
		\label{eq_dilation_case2}
		u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
		\end{equation}

		Based on the accuracy property of exponential mechanism:
		\begin{equation*}
		\begin{split}
		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
		\end{split}
		\end{equation*}
		we derived the accuracy bound for $\hexpmech$:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] 
		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
		\end{split}
		\end{equation*}

		apply this bound to eq. \ref{eq_dilation_case2}:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
		\end{split}
		\end{equation*}

		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs), \dataobs) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.

@@

	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(r, \dataobs)$, $U_1 = u(z, \dataobs') - u(z, \dataobs$), $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,

	Given that $2\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = u(r, \dataobs)]$, let $U = u(\dataobs,r)$, $U_1 = u(z, \dataobs') - u(z, \dataobs)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
	& = 	\frac{1}{|z|}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U]\Big)\\
	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U_2]\Big)\\
	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(z,, \dataobs') = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ z = r] + \delta,
	\end{split}
	\end{equation*}
	where the $\delta = \frac{e^{\epsilon/2} \delta'}{2|z|}$.
